Predicting trends in the quality of state-of-the-art neural networks without access to training or testing data

### 2021-01-01 submission/NatCom_appendix.tex
updating tables

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Dataset & $\#$ of Models \\
\hline
imagenet-1k   &  76 \\
svhn          &  30 \\
cifar-100     &  26 \\
cifar-10      &  18 \\
cub-200-2011  &  12 \\
\hline
\end{tabular}
\end{center}
\caption{Datasets used}
\label{table:datasets}
\end{table}

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{3in}|c|}
\hline
Architecture & $\#$ of Models \\
\hline
ResNet                                     & 30 \\
SENet/SE-ResNet/SE-PreResNet/SE-ResNeXt    & 24 \\
DIA-ResNet/DIA-PreResNet                   & 18 \\
ResNeXt                                    & 12 \\
WRN                                        & 12 \\
DLA                                        & 6 \\
PreResNet                                  & 6 \\
ProxylessNAS                               & 6 \\
VGG/BN-VGG                                 & 6 \\
IGCV3                                      & 6 \\
EfficientNet                               & 6 \\
SqueezeNext/SqNxt                          & 6 \\
ShuffleNet                                 & 6 \\
DRN-C/DRN-D                                & 6 \\
ESPNetv2                                   & 6 \\
HRNet                                      & 6 \\
SqueezeNet/SqueezeResNet                   & 6 \\
\hline
\end{tabular}
\end{center}
\caption{Architectures used}
\label{table:architectures}
\end{table}

>>>>

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|}
\hline
Dataset & $\#$ of Models \\
\hline
imagenet-1k   &  76 \\
svhn          &  30 \\
cifar-100     &  26 \\
cifar-10      &  18 \\
cub-200-2011  &  12 \\
\hline
\end{tabular}
\end{center}
\caption{Datasets used \charles{This table needs updated}}
\label{table:datasets}
\end{table}

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Architecture & $\#$ of Models & Datasets & & & & \\
\hline
  & total &imagenet-1k & cifar-10 & cifar-100 & svhn & cub-200-2011 \\
\hline
ResNet & 51 &22 & 8 & 8 & 7 & 6 \\
EfficientNet & 20 &20 & 0 & 0 & 0 & 0 \\
PreResNet & 14 &14 & 0 & 0 & 0 & 0 \\
VGG/BN-VGG & 12 &12 & 0 & 0 & 0 & 0 \\
ShuffleNet & 12 &12 & 0 & 0 & 0 & 0 \\
DLA & 10 &10 & 0 & 0 & 0 & 0 \\
HRNet & 9 &9 & 0 & 0 & 0 & 0 \\
DRN-C/DRN-D & 7 &7 & 0 & 0 & 0 & 0 \\
SqueezeNext/SqNxt & 6 &6 & 0 & 0 & 0 & 0 \\
ESPNetv2 & 5 &5 & 0 & 0 & 0 & 0 \\
SqueezeNet/SqueezeResNet & 4 &4 & 0 & 0 & 0 & 0 \\
IGCV3 & 4 &4 & 0 & 0 & 0 & 0 \\
ProxylessNAS & 4 &4 & 0 & 0 & 0 & 0 \\
DIA-ResNet/DIA-PreResNet & 24 &0 & 8 & 8 & 8 & 0 \\
SENet/SE-ResNet/... & 20 &0 & 5 & 5 & 4 & 6 \\
WRN & 8 &0 & 0 & 4 & 4 & 0 \\
ResNeXt & 4 &0 & 0 & 0 & 4 & 0 \\
\hline
\end{tabular}
\end{center}
\caption{Architectures used in total and per dataset \charles{I need to double check this}}
\label{table:architectures}
\end{table}
